Sound Automated Synthesis of Digital Controllers

### 2016-10-08 paper/paper.tex

\paragraph{General architecture of the program synthesiser}
%
\red{[I would recommend to clarify the domain of definition of $\sigma$, particularly over the set where $x$ ranges over. 
(Be cognisant that control audience might be unfamiliar with the cegis architecture.) ]}
% 
The design of our synthesiser is given in
Fig.~\ref{fig:CEGIS} and consists of two phases, {\sc
Synthesise} and {\sc Verify}, which interact via a finite set of test vectors {\sc inputs} \blue{that is updated incrementally}.
The {\sc synth} procedure tries to find an existential witness $P$
that satisfies the specification $\sigma(x, P)$ for all $x$, namely:
%
$\exists P . \forall x \in \text{\sc inputs} . \sigma(x, P)$

@@

If this formula is unsatisfiable, the candidate solution is in fact a
solution to the synthesis formula and so the algorithm terminates. 
Otherwise, the witness $x$ is an input on which the candidate solution fails
to meet the specification.  This witness $x$ is added to the {\sc inputs}
set, and the loop iterates again.  It is worth noting that each iteration of the
loop adds a new input to the \red{finite} set $\text{\sc inputs}$  being used for synthesis.  If
the full set of inputs \blue{[which by now should have a name, as suggested to be introduced above]} is finite, this means that the refinement loop
can only iterate a finite number of times.

@@

We use this method to check the stability in the $z$-domain for the characteristic polynomial $S(z)$ of 
the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$ \red{[unclear: what matrix? We need to clarify the relationship between the char. poly. $S(z)$ and the later quantities $\Delta N_{G}(z), \Delta D_{G}(z)$ and corresponding controller's structure.]}. 
We consider the following form for $S(z)$:
%
$$
S(z) = a_0Z^N+a_1z^{N-1}+\cdots+a_{N-1}z+a_N=0, a_0\neq0
$$
%
%\cdsay{is this for the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$?}

@@

In the {\sc verify} phase, if the system is unstable for the current candidate solution,
{\it i.e.}, if $\neg \phi_{stability}$ is satisfiable for $S(z)$, 
then we obtain a counterexample denoted by 
values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$ \red{[see my comment above - these quantities pop up too abruptly.]},
which make the closed-loop system unstable. This uncertainty is added to 
the set {\sc inputs} such that, in the subsequent {\sc synthesise} phase, 
we obtain a candidate solution consisting 
of a controller $D_C$ and $N_C$, which makes the closed-loop 
system stable for all the uncertainties accumulated in {\sc inputs}.

\paragraph{Program synthesis for the running example}
We will illustrate our synthesis approach on the running example 
in Sec.~\ref{sec:running-ex}.
We start with a candidate solution that has all coefficients 0 \red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.
In the first {\sc verify} phase we obtain the following counterexample:
$$
\begin{array}{ll}
\Delta N_G(z) = 0.02634525299072265625\\
\Delta D_G(z) = 0.9979267120361328125z-0.99768829345703125
\end{array}
$$

>>>>

\paragraph{General architecture of the program synthesiser}
%
\red{[I would recommend to clarify the domain of definition of $\sigma$, particularly over the set where $x$ ranges over. 
(Be cognisant that control audience might be unfamiliar with the cegis architecture.) ]}
% 
The design of our synthesiser is given in
Fig.~\ref{fig:CEGIS} and consists of two phases, {\sc
Synthesise} and {\sc Verify}, which interact via a finite set of test vectors {\sc inputs} 
that is updated incrementally.
Given a specification $\sigma$ over variables $x$
and $P$, the {\sc synth} procedure tries to find an existential witness $P$
that satisfies the specification $\sigma(x, P)$ for all $x$, namely:
%
$\exists P . \forall x \in \text{\sc inputs} . \sigma(x, P)$

@@

If this formula is unsatisfiable, the candidate solution is in fact a
solution to the synthesis formula and so the algorithm terminates. 
Otherwise, the witness $x$ is an input on which the candidate solution fails
to meet the specification.  This witness $x$ is added to the {\sc inputs}
set, and the loop iterates again.  It is worth noting that each iteration of the
loop adds a new input to the finite set $\text{\sc inputs}$  being used for synthesis.  If
the full set of inputs \blue{[which by now should have a name, as suggested to be introduced above]} is finite, this means that the refinement loop
can only iterate a finite number of times.

@@

We use this method to check the stability in the $z$-domain for the characteristic polynomial $S(z)$ of 
the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$, where $Y(z)$ is the 
closed-loop system output and U(z) is the controller output. 
%% \red{[unclear: what matrix? We need to clarify the relationship between the char. poly. $S(z)$ and the later quantities $\Delta N_{G}(z), \Delta D_{G}(z)$ and corresponding controller's structure.]}.
%
We consider the following form for $S(z)$:
%
$$
S(z) = a_0Z^N+a_1z^{N-1}+\cdots+a_{N-1}z+a_N=0, a_0\neq0
$$
%
%\cdsay{is this for the matrix $\left( \begin{array}{c} Y \\ U \end{array}\right)$?}

Assuming that $\hat{G}(z) = \frac{\hat{N_G}(z)}{\hat{D_G}(z)}$
and $\hat{C}(z) = \frac{\hat{N_C}(z)}{\hat{D_C}(z)}$, then:
$$S(z) = FWL[N_C(z)] \times \hat{N_G}(z) + FWL[D_C(z)] \times \hat{D_G}(z)$$

@@

In the {\sc verify} phase, if the system is unstable for the current candidate solution,
{\it i.e.}, if $\neg \phi_{stability}$ is satisfiable for $S(z)$, 
then we obtain a counterexample denoted by 
values for each coefficients of $\Delta N_{G}(z)$ and $\Delta D_{G}(z)$, 
%\red{[see my comment above - these quantities pop up too abruptly.]},
which make the closed-loop system unstable. 
Note that, similar to the rest of the paper, we use the notation 
$\hat{N_G}(z) = N_G(z) + \Delta N_G(z)$ and 
$\hat{N_C}(z) = N_C(z) + \Delta N_C(z)$.
This uncertainty is added to 
the set {\sc inputs} such that, in the subsequent {\sc synthesise} phase, 
we obtain a candidate solution consisting 
of a controller $D_C$ and $N_C$, which makes the closed-loop 
system stable for all the uncertainties accumulated in {\sc inputs}.

\paragraph{Program synthesis for the running example}
We will illustrate our synthesis approach on the running example 
in Sec.~\ref{sec:running-ex}.
We start with a candidate solution that has all coefficients 0:
%\red{[Be more explicit, write out spurious candidate solution with zero coefficients. KISS - you don't want to lose the control audience here.]}.

$$
\begin{array}{ll}
N_C(z) {=} 0z^2{+}0z{+}0\\
D_C(z) {=} 0z^2{+}0z{+}0\\
\end{array}
$$

In the first {\sc verify} phase we obtain the following counterexample:
$$
\begin{array}{ll}
\Delta N_G(z) = 0.02634525299072265625\\
\Delta D_G(z) = 0.9979267120361328125z-0.99768829345703125
\end{array}
$$
